%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-0.3cm}
\begin{small}\textit{* presenting author; \textsuperscript{+} mentored undergraduate}\end{small}

%-------------------------------------------------------------------------------
% \cvsubsection{Invited Talks}
% %-------------------------------------------------------------------------------

% \begin{cvpubs}
%     \cvpub {Spring 2019. \textit{Title of my fancy talk}. Invited talk: Event That I Presented At, City, State.}
    
%     \cvpub{Spring 2018. \textit{A guest lecture for a course}. Guest Lecture, Name of Course, University.}
    
%     \cvpub{Spring 2018. \textit{A different invited talk that I gave}. Invited talk: Event I Presented At, City, State.}
% \end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Contributed Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}


   % \cvpub{\textbf{Name, Y}, Author Two. 2018. A poster that I presented with only myself and my advisor as authors. Poster: The Conference I Presented At, City, State.}
              \cvpub{\textbf{Diana W Dawoud}*, Fabien Heliot, Muhammad Ali Imran, and Rahim Tafazolli. 2017, Spatial quadrature modulation for visible
light communication in indoor environment. Oral presentation: IEEE International Conference on Communications (ICC), Paris, France.}

    \cvpub{\textbf{Diana W Dawoud}*, Fabien Héliot, Muhammad Ali Imran, and Rahim Tafazolli. 2018. A Novel Orthogonal Transmission Scheme for Visible Light Communication. Oral presentation: IEEE International Conference on Communications (ICC), Kansas City, USA.}


     \cvpub{\textbf{Diana W Dawoud}*, Fabien Héliot, Muhammad Ali Imran, and Rahim Tafazolli. 2018.Low-complexity detection scheme for p-
orthogonal transmission method. 2021, Oral presentation: 4th International Conference on Signal Processing and Information Security
(ICSPIS), Dubai, UAE.}

  %  \cvpub{\textbf{Name, Y}. 2015. A different departemental seminar that I gave. Departmental seminar: University's Department, City, State.}

  %  \cvpub{Undergrad, Y*\textsuperscript{+}, \textbf{Your Name}, Author Three, Author Four. 2015. Title of a poster presented by an undergrad I mentored. Poster: Event Presented At, City, State.}



        \cvpub{Shereen Ismail*\textsuperscript{+}, \textbf{Diana W Dawoud}, and Hassan Reza. A lightweight multilayer machine learning detection system for cyber-
attacks in WSN. 2022, Oral presentation: IEEE 12th annual computing and communication workshop and conference (CCWC), USA.}

     \cvpub{Shereen Ismail*\textsuperscript{+}, \textbf{Diana W Dawoud}, and Hassan Reza. Towards a lightweight identity management and secure authentication
for iot using blockchain. 2022, Oral presentation:  IEEE World AI IoT Congress (AIIoT), USA.}

     \cvpub{Shereen Ismail*\textsuperscript{+} and \textbf{Diana W Dawoud}. Software development models for iot. 2022, Oral presentation:  IEEE 12th Annual Computing and
Communication Workshop and Conference (CCWC), USA.}
     
     \cvpub{Rasha Ghabboun, \textbf{Diana W Dawoud}, Eman Abu Shabab, and Shereen Ismail *\textsuperscript{+}. Adaptive real-time speed limit broadcasting
for autonomous driving applications using visible light communication. 2023, Oral presentation:  IEEE International Conference on Electro
Information Technology (eIT), USA.}

     \cvpub{Shereen Ismail*\textsuperscript{+}, \textbf{Diana W Dawoud}, Tamara Al-Zyoud, and Hassan Reza. Towards blockchain-based adaptive trust manage-
ment in wireless sensor networks. 2023, Oral presentation: IEEE International Conference on Electro Information Technology (eIT), USA.}



\end{cvpubs}
