%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\cvsubsection{Patent}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Diana W. Dawoud}, Fabien Heliot, and Muhammad Ali Imran. Transmitting and receiving symbols via unipolar signals, Septem-
ber 20 2022. US Patent 11,451,296}
    \end{cvpubs}
%---------------------------------------------------------
 \cvsubsection{Journal}
% %---------------------------------------------------------

\begin{cvpubs}
     \cvpub{\textbf{Diana W. Dawoud}, Fabien Héliot, Muhammad Ali Imran, and Rahim Tafazolli. A novel unipolar transmission scheme for
visible light communication. IEEE Transactions on Communications, 68(4):2426–2437, 2019}
    
    \cvpub{Shereen Ismail, \textbf{Diana W. Dawoud}, Nadhem Ismail, Ronald Marsh, and Ali S Alshami. IoT-based water management systems:
Survey and future research direction. IEEE Access, 10:35942–35952, 2022}

     \cvpub{Shereen Ismail, \textbf{Diana W. Dawoud}, and Hassan Reza. Securing wireless sensor networks using machine learning and blockchain:
A review. Future Internet, 15(6):200, 2023}

     \cvpub{Oussama Kerdjidj, Yassine Himeur, Shahab Saquib Sohail, Abbes Amira, Fodil Fadli, Shadi Atalla, Wathiq Mansoor, Abigail
Copiaco, Mohammad Daradkeh, Amjad Gawanmeh, Sami Miniaoui, and \textbf{Diana W. Dawoud}. Uncovering the potential of
indoor localization: Role of deep and transfer learning. 2023}
 \end{cvpubs}   
    

% % %---------------------------------------------------------
  \cvsubsection{Conferences}
% % % %---------------------------------------------------------
\begin{cvpubs}

     \cvpub{Hanaa Marshoud, \textbf{Diana W. Dawoud}, Vasileios M Kapinas, George K Karagiannidis, Sami Muhaidat, and Bayan Sharif. Mu-MIMO
precoding for vlc with imperfect csi. In 2015 4th International Workshop on Optical Wireless Communications (IWOW),
pages 93–97. IEEE, 2015}

     \cvpub{\textbf{Diana W. Dawoud}, Fabien Héliot, Muhammad Ali Imran, and Rahim Tafazolli. Spatial quadrature modulation for visible
light communication in indoor environment. In 2017 IEEE International Conference on Communications (ICC), pages
1–6. IEEE, 2017}
     
     \cvpub{\textbf{Diana W. Dawoud}, Fabien Heliot, Muhammad Ali Imran, and Rahim Tafazolli. A novel orthogonal transmission scheme for
visible light communication. In 2018 IEEE International Conference on Communications (ICC), pages 1–6. IEEE, 2018}

     \cvpub{Eman Hasan, Khaled Al-Wahedi, Belal Jumah, \textbf{Diana W. Dawoud}, and Jorge Dias. Circle formation in multi-robot systems
with limited visibility. In ROBOT 2017: Third Iberian Robotics Conference: Volume 1, pages 323–336. Springer, 2018}

     \cvpub{\textbf{Diana W. Dawoud}, Fabien Héliot, Muhammad Ali Imran, and Rahim Tafazolli. Low-complexity detection scheme for p-
orthogonal transmission method. In 2021 4th International Conference on Signal Processing and Information Security
(ICSPIS), pages 76–79. IEEE, 2021}
     
     \cvpub{Muna Darweesh and \textbf{Diana W. Dawoud}. Simple lifi oximeter monitoring system for telehealth applications. In 2021 28th
IEEE International Conference on Electronics, Circuits, and Systems (ICECS), pages 1–4. IEEE, 2021}

     \cvpub{Shereen Ismail, \textbf{Diana W. Dawoud}, and Hassan Reza. A lightweight multilayer machine learning detection system for cyber-
attacks in wsn. In 2022 IEEE 12th annual computing and communication workshop and conference (CCWC), pages 0481–
0486. IEEE, 2022}

     \cvpub{Shereen Ismail, \textbf{Diana W. Dawoud}, and Hassan Reza. Towards a lightweight identity management and secure authentication
for iot using blockchain. In 2022 IEEE World AI IoT Congress (AIIoT), pages 077–083. IEEE, 2022}

     \cvpub{Shereen Ismail and \textbf{Diana W. Dawoud}. Software development models for iot. In 2022 IEEE 12th Annual Computing and
Communication Workshop and Conference (CCWC), pages 0524–0530. IEEE, 2022
MARCH 2019}
     
     \cvpub{Rasha Ghabboun, \textbf{Diana W. Dawoud}, Eman Abu Shabab, and Shereen Ismail. Adaptive real-time speed limit broadcasting
for autonomous driving applications using visible light communication. In 2023 IEEE International Conference on Electro
Information Technology (eIT), pages 191–196. IEEE, 2023}

     \cvpub{Shereen Ismail, \textbf{Diana W. Dawoud}, Tamara Al-Zyoud, and Hassan Reza. Towards blockchain-based adaptive trust manage-
ment in wireless sensor networks. In 2023 IEEE International Conference on Electro Information Technology (eIT), pages
163–168. IEEE, 2023}
  \end{cvpubs}

% % % %---------------------------------------------------------
\cvsubsection{Under Development}
% % %---------------------------------------------------------

 \begin{cvpubs}
 \small \color{black}
     \cvpub{Performance Evaluation of Key-Based Physical Layer Security in Visible Light Communication Systems }

     \cvpub{Energy Efficient Scheme for High-Speed DSOC}

     \cvpub{Advancing Passenger Experience and Reliability of Autonomous Buses Through LiFi Technology}

     \cvpub{A Comparative Study of Datasets for Cyber-attacks Detection in Wireless Sensor Networks}
     \cvpub{Perceptions, Attitudes, and Demographic Influences on
Metaverse: A Comprehensive Investigation]{Perceptions, Attitudes, and Demographic Influences on
Metaverse: A Comprehensive Investigation}

\cvpub{Zero Trust Blockchain Supply Chain}

     \end{cvpubs}

% % %---------------------------------------------------------




